\section{Material und Methoden}
First order and second order antibodies of different animals types um die Signalstärke zu erhöhen, da Alexa Fluorophor \underline{'anti ANIMAL Type'} zum  first order antibody ist und somit sonnst an beiden verschieden markierten alpha-Tubuilin und detyr-tubulin binden kann.\\\\
TrackMate \cite{Ershov_2021} \cite{Tinevez_2017} \\
'LysoTracker™ Green DND-26 is a green fluorescent dye that stains acidic compartments in live cells with excitation/emission maxima ∼504/511 nm.' \url{https://www.thermofisher.com/order/catalog/product/L7526}
\\
'SiR-tubulin is based on the far-red silicon rhodamine (SiR) fluorophore analogue SiR and the microtubule-binding drug Docetaxel. SiR-tubulin allows labeling of endogenous microtubules in live cells with high specificity and low background without the need for genetic manipulation or over-expression. The key features of SiR-tubulin are i) far-red absorption and emission wavelengths, ii) cell permeability, iii) fluorogenic character, and iv) compatibility with super-resolution microscopy (e.g., STED & SIM). In addition, SiR-tubulin can be used for wide-field and confocal fluorescent imaging in living cells. The emission in the far-red wavelength minimizes phototoxicity and sample autofluorescence.' \url{https://www.cytoskeleton.com/tubulins/live-cell-imaging-tubulin/cy-sc014}
\\\\
'Immunocytochemistry (ICC) is a common laboratory technique that is used to anatomically visualize the localization of a specific protein or antigen in cells by use of a specific primary antibody that binds to it. The primary antibody allows visualization of the protein under a fluorescence microscope when it is bound by a secondary antibody that has a conjugated fluorophore.' \url{https://en.wikipedia.org/wiki/Immunocytochemistry}\\\\
Blocken verhindert unspezifische Bindung und erlaubt somit nur spezifische Bindung der Antikörper \\\\
Spinning disk confocal microscopy (SDCM) löst das Problem der geringen Zeitauflösung des Laser Scanning Confocal Microscope (LSCM), indem es eine Nipkow-Scheibe verwendet. Die Scheibe besitzt viele Lochblenden. Diese Scheibe wird bei der Untersuchung rotiert, wodurch die Beobachtungsebene wie homogen beleuchtet ist. With that you can capture a large field of view (FOV) in as little as 5ms, but with a lost of intensity due to light scattering.

%\url{https://zeiss-campus.magnet.fsu.edu/articles/spinningdisk/introduction.html}
\\
TIRFM stands for 'Total Internal Reflection Fluorescence Microscopy'. Effekt der Totalreflexion wird ausgenutzt, um oberflächennahe Prozess zu studieren. Die evaneszente Welle hat eine Eindringstiefe von ca. 100-200nm und regt nur die Fluorophore in diesen Bereich an. Die Methode wird zur Untersuchung der Unterseite von adhärenten Zellen verwendet.

\newpage